\documentclass[5p,twocolumn,times,number]{elsarticle}

\usepackage{graphicx}
\usepackage{amsmath}   

\begin{document}

\begin{frontmatter}

\title{Progress on BaF$_2$ Crystals and Photosensors}

\author{C.-h. Cheng}
\author{K.~Flood}
\author{H. Gestsson}
\author{D.G Hitlin}
\author{J.H. Kim}
\author{F.C. Porter}
\author{J. Trevor}



\address{Caltech}


\begin{abstract}
We summarize herein progress on the measurement of barium fluoride crystal properties, including light yield, transmission, radiation hardness and cost, as well as on the devlopment of an avalanche photodiode sensor that is sensitive only to the fast scintillation component of Ba F$_2$.

\end{abstract}


\end{frontmatter}



\section{Introduction}


\section{Higher Rate Running}


\section{Conclusion}



%\section*{Acknowledgments}



%% bibliography
\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi

\bibitem{Sauli:1997qp}
F.~Sauli, {GEM}: A new concept for electron amplification in gas detectors,
  Nucl. Instrum. Meth. A386 (1997) 531--534.

\bibitem{Altunbas:2002ds}
M.~C. Altunbas, et~al., Construction, test and commissioning of the
  triple-{GEM} tracking detector for {COMPASS}, Nucl. Instrum. Meth. A490
  (2002) 177--203.

\bibitem{Simon:2007sk}
F.~Simon, et~al., {Development of Tracking Detectors with industrially produced
  GEM Foils}, IEEE Trans. Nucl. Sci. 54 (2007) 2646--2652.

\bibitem{Simon:2007fz}
F.~Simon, The {STAR} tracking upgrade, arXiv:0710.0172 [physics.ins-det].

\bibitem{Ackermann:2002ad}
K.~H. Ackermann, et~al., {STAR} detector overview, Nucl. Instrum. Meth. A499
  (2003) 624--632.

\bibitem{Allgower:2002zy}
C.~E. Allgower, et~al., The {STAR} endcap electromagnetic calorimeter, Nucl.
  Instrum. Meth. A499 (2003) 740--750.

\end{thebibliography}

\end{document}
